---
title: "1.25 Chap3"
author: "Jo, Munsun"
date: '2022 1 25 '
output: rmarkdown::github_document
---


# Chap3

## 1. Create Table using data.frame
```{r}
state=c('Connecticut','Maine','Maassachusetts','New Hampshire','Rhode Island','Vermont')
Total_Teachers=c(42,17,69,15,11,8)
popu=c(35,13,64,13,11,6)
df=data.frame(state, Total_Teachers, popu)
```

## 2. With or Without replacement
### Generate ALL Combinations of N Elements, Taken n at a Time
### expand.grid for creating a data frame from all combinations of factors or vectors.
```{r}
sample=t((combn(1:N,n))) # t means to transpose
sample=t((combn(1:4,2)))
```

### list of samples of size n with replacement from N units
```{r}
sample=expand.grid(1:N,1:N,1:N) # e.g. n=3
sample=expand.grid(1:4,1:4) # N=4, n=2
```
  
## 3. lecture note: Discrete finite population using unequal prob sampling without replacement
```{r}
u=c(1,2,3,4)
N=4
n=2
sample=t((combn(1:4,2)))
ps=c(1/3,1/6,0,0,0,1/2) # ps denotes the probability of sample
```

### Calculate inclusion probability pi_i
```{r}
pi=rep(0,length(u))
for (i in 1:length(u)){
  pi[i]=sum(ps[sample[,1]==i])+sum(ps[sample[,2]==i])
}
```

## 4. Lecture note: sample n=2 with varying probability and with replacement
```{r}
u=c(1,2,3,4)
delta=c(0.1, 0.1, 0.4, 0.4)
sample=expand.grid(1:4, 1:4) # N=4, n=2
```

### Calculate probability of sample, denoted by ps
```{r}
ps=rep(0, dim(sample)[1])
ps=delta[sample[,1]]*delta[sample[,2]] # delta[put in the index]
hat_tau=1/2*(sample[,1]/delta[sample[,1]]+sample[,2]/delta[sample[,2]])
df=data.frame(sample, ps, hat_tau)
```

#### Expectation of hat_tau
```{r}
ps%*%hat_tau # matrix multiplication
```

## 5. Lecture note: sample n=2 with varying probability and **without** replacement
### also see textbook page 56: Table 3.2
```{r}
u=c(1,2,3,4)
delta=c(0.1, 0.1, 0.4, 0.4)
sample=t(combn(1:4, 2))
```

### step 1: Calculate probability of sample, denoted by ps
```{r}
ps=rep(0, dim(sample)[1])
ps=delta[sample[,1]]*delta[sample[,2]]/(1-delta[sample[,1]])+delta[sample[,2]]*delta[sample[,1]]/(1-delta[sample[,2]])
```

### step 2: Calculate inclusion probability pi_i
```{r}
pi=rep(0, length(u))
for (i in 1:length(u)){
  pi[i]=sum(ps[sample[,1]==i])+sum(ps[sample[,2]==i])
}
```

### step 3: Calculate hat_tao using pi_i
```{r}
hat_tau=rep(0, dim(sample)[1])
hat_tau=u[sample[,1]]/pi[sample[,1]]+u[sample[,2]]/pi[sample[,2]]
```

### step 4: Expectation of hat_tao
```{r}
ps%*%hat_tau
```
